---  
title: "hierSCAL OM fit report"
geometry: letterpaper
nocaption: false
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{caption}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
always_allow_html: yes
params:
  batchDir: "~/Work/code/models/stockAssessment/multispecies/hierSCAL/Outputs/fits/April26"
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: kable
    keep_md: false
  word_document:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
  bookdown::pdf_document2:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
    fig_width: 7
    fig_height: 6
  bookdown::html_document2:
    self_contained: true
    df_print: kable
    keep_md: false
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
  bookdown::word_document2:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
---

# Data Scenario and Model Hypothesis

```{r, setup, message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}

# I usually load my libraries up front to keep things organized
library( bookdown )
library( knitr )
library( kableExtra )
library( dplyr )
library( stringr )
library( tidyverse )
library( here )
library( ggridges )
library( ggsidekick )

knitr::opts_knit$set( fig.pos = 'p',
                      out.width = '100%', dpi=300, 
                      root.dir = params$batchDir,
                      message = FALSE, warning = FALSE, echo = FALSE )

options(warn = -1)

source(here("plots.R"))
source(here("SCALfuns.R"))
source(here("SCALtools.R"))
source(here("refPts.R"))

# Count the number of fits in the batch directory
info.df <- readBatchInfo(params$batchDir)


```

Comparison of model fits for hierSCAL fit to DERPA data 
under multiple data scenarios and model hypotheses.

Batch folder: `r params$batchDir`




```{r, captions, include = FALSE, echo = FALSE}
SBsptCaption <- "Comparison of spawning biomass"

StdIdxCap   <- "Standardised vulnerable biomass (coloured lines) and the scaled and standardised biomass indices they are fitting to (coloured points), for all stocks and species."

IdxResCap   <- "Standardised residuals for model fits to biomass indices (coloured points) and a loess smoother with a 20% confidence interval (coloured lines and grey regions), for all fleets, stocks, and species."

RecPlotCap <- "Age-1 recruitments for all species and stocks. Equilibrium unfished recruitment $R_0$ is indicated by the horizontal dashed line."

RecDevPlotCap <- "Deviations from expected recruitment for all species and stocks."

YeqFCurvesCap <- "Equilibrium yield curves as a function of fishing mortality rates, assuming all fishing mortality comes from the modern trawl fleet."

ProbLenAgeCap <- "Probability curves of length-at-age for males (blue) and females (red). Curves show the probability of each length within an age group, and opacity of the lines increases with age."

tvqCap <- "Time series of observation model catchability (log-scale, coloured points) for the commercial fleets and Hecate Strait Multispecies Assemblage survey. Lines show the smoothed trend using a Loess smoother"

fishingMortCap <- "Estimates of fishing mortality from each fleet (coloured points and lines), gridded over species (columns) and stocks (rows). Fishing mortality rates are found using an iterative Newton-Rhapson solver conditioned on the observed catch."

modeledCatchCap <- "Modeled removals (blue points) using estimated fishing mortality compared to observed catches (open circles), gridded over species (columns) and stocks (rows)."

SRplotCap <- "Stock-recruit curves (solid lines) and modeled recruitments (grey points), gridded over species (columns) and stocks (rows)."

selLenCap <- "Selectivity-at-length for each fleet, gridded over species (columns) and stocks (rows). "

selAgeCap <- "Selectivity-at-age for each fleet, for females only, gridded over species (columns) and stocks (rows). "

```


# Full complex

## Spawning Biomass

```{r, plotSBall, echo = FALSE, message = FALSE, fig.cap = SBsptCaption }
plotSBspt( repObj = repObj, initYear = fYear)
```


## Fits to indices

```{r, idxFitsall, echo = FALSE, fig.cap = StdIdxCap }
plotScaledIdxGrid( repObj = repObj )

```

```{r, idxResidsAll, echo = FALSE, fig.cap = IdxResCap }
plotIdxResidsGrid( repObj = repObj )

```

## Recruitment

```{r, recruitments, echo = FALSE, fig.cap = RecPlotCap }
plotRspt( repObj = repObj, initYear = fYear )
```

```{r, recruitmentDevs, echo = FALSE, fig.cap = RecDevPlotCap }
plotRsptDev( repObj = repObj, initYear = fYear )
```

```{r, stockRecCurves, echo = FALSE, fig.cap = SRplotCap }
plotSRsp( repObj = repObj, initYear = fYear )
```


## Time-varying catchability

```{r, tvq, echo = FALSE, fig.cap = tvqCap }
plotTVq( repObj = repObj, sIdx = 1:nS, pIdx = 1:nP )
```

## Fishing mortality

```{r, fishingMortPlot, echo = FALSE, fig.cap = fishingMortCap }
  plotFspft( repObj = repObj, initYear = fYear )
```

```{r, catchFitPlot, echo = FALSE, fig.cap = modeledCatchCap }
  plotCatchFit_spt( repObj = repObj, initYear = fYear )
```


## Growth (Probability of Length-at-age)

```{r, plotProbLenAge, echo = FALSE, fig.cap = ProbLenAgeCap}
plotProbLenAge_sp(repObj)
```

## Selectivity

```{r, plotSelLength, echo = FALSE, fig.cap = selLenCap }
plotSelLen_spf(repObj = repObj, sIdx = 1:nS, pIdx = 1:nP )
```

```{r, plotSelAge, echo = FALSE, fig.cap = selAgeCap }
plotSelAge_spf(repObj = repObj, sIdx = 1:nS, pIdx = 1:nP )
```

## Reference Points

### Yield Curves

```{r, YeqFCurves, fig.cap = YeqFCurvesCap, echo = FALSE}
nS      <- repObj$nS
nP      <- repObj$nP
plotYeqF(repObj = repObj, sIdx = 1:nS, pIdx = 1:nP)


```

### Goldilocks Plots



### Table

```{r, FmsyRefPtsTable, echo = FALSE}

FmsyRefPts <- repObj$refPts$FmsyRefPts

# need to combine these all into a table - also want B0/R0 etc
B0_sp       <- round(repObj$B0_sp,2)
R0_sp       <- round(repObj$R0_sp,2)
h_sp        <- round(repObj$h_sp,2)
M_spx       <- round(repObj$M_spx,2)
Bmsy_sp     <- round(FmsyRefPts$BeqFmsy_sp,2)
Fmsy_sp     <- round(FmsyRefPts$Fmsy_sp,2)
Umsy_sp     <- round(FmsyRefPts$Umsy_sp,2)
MSY_sp      <- round(FmsyRefPts$YeqFmsy_sp,2)
SSBT_sp     <- round(repObj$SB_spt[,,nT,drop = FALSE],2)
DT_sp       <- round(SSBT_sp[,,1]/B0_sp,2)
DmsyT_sp    <- round(SSBT_sp[,,1]/Bmsy_sp,2)

nTabRow <- nS * nP
nTabCol <- 14
refPtsTab <- matrix(NA, nrow = nTabRow, ncol = nTabCol )
colnames(refPtsTab) <- c( "Species",
                          "Stock",
                          "B0",
                          "R0",
                          "M_m",
                          "M_f",
                          "h",
                          "Bmsy",
                          "Fmsy",
                          "Umsy",
                          "MSY",
                          "SSB_T",
                          "D_T",
                          "Dmsy_T" )

for( s in 1:nS )
  for(p in 1:nP )
  {
    rowIdx <- (s - 1) * nP + p

    refPtsTab[rowIdx,"Species"]  <- species[s]
    refPtsTab[rowIdx,"Stock"]    <- stock[p]
    refPtsTab[rowIdx,"B0"]       <- B0_sp[s,p]
    refPtsTab[rowIdx,"R0"]       <- R0_sp[s,p]
    refPtsTab[rowIdx,"M_m"]      <- M_spx[s,p,1]
    refPtsTab[rowIdx,"M_f"]      <- M_spx[s,p,2]
    refPtsTab[rowIdx,"Bmsy"]     <- Bmsy_sp[s,p]
    refPtsTab[rowIdx,"Fmsy"]     <- Fmsy_sp[s,p]
    refPtsTab[rowIdx,"Umsy"]     <- Umsy_sp[s,p]
    refPtsTab[rowIdx,"MSY"]      <- MSY_sp[s,p]
    refPtsTab[rowIdx,"SSB_T"]    <- SSBT_sp[s,p,1]
    refPtsTab[rowIdx,"D_T"]      <- DT_sp[s,p]
    refPtsTab[rowIdx,"Dmsy_T"]   <- DmsyT_sp[s,p]

  }

# Kable that table!
kable(  refPtsTab, escape = FALSE, 
        caption = "Biological reference points for each stock and species.", booktabs = T,
        align = rep("c",ncol(refPtsTab))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))

```



## Correlations

**UNDER CONSTRUCTION**

# Individual species

**UNDER CONSTRUCTION**

## Compositional data

## Growth


# Optimisation performance

## Phase fit table

```{r, phaseTable, echo = FALSE }
phaseReportTable <- reports$phaseList$fitReport

kable(  phaseReportTable, escape = FALSE, 
        caption = "Optimisation performance of hierSCAL for each phase.", booktabs = T,
        align = rep("c",ncol(phaseReportTable))) %>%
  kable_styling(latex_options = c("striped", "scale_down","hold_position"),
                bootstrap_options = c("striped", "hover"))

```


