---  
title: "hierSCAL OM fit report"
geometry: letterpaper
nocaption: false
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{caption}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
always_allow_html: yes
params:
  rootDir: "~/Work/code/models/stockAssessment/multispecies/ms3R/Outputs/sim_11122019143054/"
  RdataFile: "sim_11122019143054.RData"
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: kable
    keep_md: false
  word_document:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
  bookdown::pdf_document2:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
    fig_width: 7
    fig_height: 6
  bookdown::html_document2:
    self_contained: true
    df_print: kable
    keep_md: false
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
  bookdown::word_document2:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
---

# Simulation details

```{r, setup, message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}

# I usually load my libraries up front to keep things organized
library(bookdown)
library(knitr)
library(kableExtra)
library(dplyr)
library(stringr)
library(tidyverse)
library(here)

knitr::opts_knit$set(   fig.pos = 'p',
                        out.width = '100%', dpi=300, 
                        root.dir = params$rootDir,
                        message = FALSE, warning = FALSE, echo = FALSE )

options(warn = -1)

source(here("ms3Rplots.R"))
source(here("tools.R"))
source(here("refPts.R"))
source(here("stats.R"))

# Read in report file

blobPath <- file.path(params$rootDir, params$RdataFile)
load(blobPath)


fYear   <- blob$ctlList$opMod$fYear
nS      <- blob$om$nS
nP      <- blob$om$nP
nT      <- blob$om$nT

species <- blob$om$speciesNames
stock   <- blob$om$stockNames

```

Standard sim report for ms3R

Scenario: `r blob$ctlList$ctl$scenarioName`

Model Hypothesis: `r blob$ctlList$ctl$mpName`

Species complex: `r blob$ctlList$data$species`

Stock areas: `r blob$ctlList$data$stocks`




```{r, captions, include = FALSE, echo = FALSE}
SBsptCaption <- "Simulation envelopes of spawning biomass and catch scaled by unfished biomass.  
Columns are species, and rows are stock areas. Median biomass is shown by the thick black lines, 
with the grey region showing the central 95% of the distribution of spawning biomass, and thin black lines showing three randomly selected
simulation replicates. Catch is shown as grey bars in the historical period, which represent
median catch in the projection, with thin vertical line segments showing the central 95%
of the catch distribution."

TACuCaption <- "Simulation envelopes of TAC utilisation. Columns are species, rows are stock 
areas. Heavy black lines show the median TAC utilisation, with thin black lines showing 3 
random replicates, and the grey region showing the central 95% of the distribution."

EffTulipCaption <- "Simulation envelopes of effort in each stock area."

convStatsCaption <- "Convergence diagnostics for the simulated assessment model at each projection time step.
The left hand column shows the distribution of maximum gradient components across replicates, 
and the right hand column shows the proportion of replicates where the AM produced a 
positive definite Hessian matrix."

# StdIdxCap   <- "Standardised vulnerable biomass (coloured lines) and the scaled and standardised biomass indices they are fitting to (coloured points), for all stocks and species."

# IdxResCap   <- "Standardised residuals for model fits to biomass indices (coloured points) and a loess smoother with a 20% confidence interval (coloured lines and grey regions), for all fleets, stocks, and species."

# RecPlotCap <- "Age-1 recruitments for all species and stocks. Equilibrium unfished recruitment $R_0$ is indicated by the horizontal dashed line."

# RecDevPlotCap <- "Deviations from expected recruitment for all species and stocks."

# YeqFCurvesCap <- "Equilibrium yield curves as a function of fishing mortality rates, assuming all fishing mortality comes from the modern trawl fleet."

# ProbLenAgeCap <- "Probability curves of length-at-age for males (blue) and females (red). Curves show the probability of each length within an age group, and opacity of the lines increases with age."

# tvqCap <- "Time series of observation model catchability (log-scale, coloured points) for the commercial fleets and Hecate Strait Multispecies Assemblage survey. Lines show the smoothed trend using a Loess smoother"

# fishingMortCap <- "Estimates of fishing mortality from each fleet (coloured points and lines), gridded over species (columns) and stocks (rows). Fishing mortality rates are found using an iterative Newton-Rhapson solver conditioned on the observed catch."

# modeledCatchCap <- "Modeled removals (blue points) using estimated fishing mortality compared to observed catches (open circles), gridded over species (columns) and stocks (rows)."

# SRplotCap <- "Stock-recruit curves (solid lines) and modeled recruitments (grey points), gridded over species (columns) and stocks (rows)."

# selLenCap <- "Selectivity-at-length for each fleet, gridded over species (columns) and stocks (rows). "

# selAgeCap <- "Selectivity-at-age for each fleet, for females only, gridded over species (columns) and stocks (rows). "

# circRecDevsCap <- "Standardised recruitment deviations. Blue indicates a positive deviation, red indicates a negative deviation, and the area of each circle is proportional to the size of the deviation."

# corrRecDevsCap <- "Correlation matrix of recruitment deviations. Blue indicates a positive correlation, and red indicates a negative correlation."

```


# Simulation envelopes

## Spawning Biomass

```{r, plotTulipBtCt, echo = FALSE, message = FALSE, fig.cap = SBsptCaption }
plotTulipBt( obj = blob, dep = TRUE, Ct = TRUE )
```

## TAC utilisation

```{r, plotTulipTACu, echo = FALSE, message = FALSE, fig.cap = TACuCaption }
plotTulipTACu( obj = blob )
```

## Effort allocation

```{r, plotTulipEffort, echo = FALSE, message = FALSE, fig.cap = EffTulipCaption }
plotTulipEffort_p( obj = blob )
```


# To be added:

- Single sim replicates with catch
- 

# Performance

## Stats table

```{r, phaseTable, echo = FALSE }

statTable <- .simPerfStats( obj = blob )

kable(  statTable, escape = FALSE, 
        caption = "Performance statistics for this simulation.", booktabs = T,
        align = rep("c",ncol(statTable))) %>%
  kable_styling( latex_options = c("striped", "scale_down","hold_position"),
                 bootstrap_options = c("striped", "hover"))

```

## Convergence diagnostics

```{r, plotConvergence, echo = FALSE, message = FALSE, fig.cap = convStatsCaption }
plotConvStats( obj = blob )
```
