---  
title: "ms3R Simulation Report"
geometry: letterpaper
nocaption: false
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{caption}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
always_allow_html: yes
params:
  rootDir: "~/Work/code/models/stockAssessment/multispecies/ms3R/Outputs/sim_11122019143054/"
  RdataFile: "sim_11122019143054.RData"
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: kable
    keep_md: false
  word_document:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
  bookdown::pdf_document2:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Work/write/templates/tex/TandF.latex
    fig_width: 7
    fig_height: 6
  bookdown::html_document2:
    self_contained: true
    df_print: kable
    keep_md: false
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
  bookdown::word_document2:
    df_print: kable
    reference_docx: /Users/sdnjohnson/Work/write/templates/docx/basic.docx
---

# Simulation details

```{r, setup, message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}

# I usually load my libraries up front to keep things organized
library(bookdown)
library(knitr)
library(kableExtra)
library(dplyr)
library(stringr)
library(tidyverse)
library(here)

knitr::opts_chunk$set(  fig.pos = 'p',
                        out.width = '100%', dpi=300, 
                        root.dir = params$rootDir,
                        message = FALSE, warning = FALSE, echo = FALSE,
                        fig.width = 12, fig.height = 8 )

options(warn = -1)

source(here("ms3Rplots.R"))
source(here("tools.R"))
source(here("ms3RrefPts.R"))
source(here("stats.R"))

# Read in report file

blobPath <- file.path(params$rootDir, params$RdataFile)
load(blobPath)


fYear   <- blob$ctlList$opMod$fYear
nS      <- blob$om$nS
nP      <- blob$om$nP
nT      <- blob$om$nT
tMP     <- blob$om$tMP

species <- blob$om$speciesNames
stock   <- blob$om$stockNames

goodReps_isp    <- blob$goodReps_isp
nGoodReps_sp    <- apply(X = goodReps_isp, FUN = sum, MARGIN = c(2,3))
allSuccessful_i <- apply(X = goodReps_isp, FUN = prod, MARGIN = 1)
goodTraceIdx    <- which(allSuccessful_i == 1)


# Draw a random replicate for plotting
set.seed(123)
randReplicate <- 1
if( sum(goodTraceIdx) > 0 )
  randReplicate <- sample(goodTraceIdx, size = 1)

```

Standard sim report for ms3R

Scenario: `r blob$ctlList$ctl$scenarioName`

Model Hypothesis: `r blob$ctlList$ctl$mpName`

Species complex: `r blob$ctlList$data$species`

Stock areas: `r blob$ctlList$data$stocks`

Min number of good replicates: `r min(nGoodReps_sp)`




```{r, captions, include = FALSE, echo = FALSE}
SBsptCaption <- "Simulation envelopes of spawning biomass and catch scaled by unfished biomass.  
Columns are species, and rows are stock areas. Median biomass is shown by the thick black lines, 
with the grey region showing the central 95% of the distribution of spawning biomass, and thin black lines showing three randomly selected
simulation replicates. Catch is shown as grey bars in the historical period, which represent
median catch in the projection, with thin vertical line segments showing the central 95%
of the catch distribution."

TACuCaption <- "Simulation envelopes of TAC utilisation. Columns are species, rows are stock 
areas. Heavy black lines show the median TAC utilisation, with thin black lines showing 3 
random replicates, and the grey region showing the central 95% of the distribution."

EffTulipCaption <- "Simulation envelopes of effort in each stock area."

FTulipCaption <- "Simulation envelopes of fishing mortality for each stock."

convStatsCaption <- "Convergence diagnostics for the simulated assessment model at each projection time step.
The left hand column shows the distribution of maximum gradient components across replicates, 
and the right hand column shows the proportion of replicates where the AM produced a 
positive definite Hessian matrix."

retroSBCaption <- "Retrospective assesment model estimates of stock biomass from a 
randomly selected simulation replicate. Red lines are spawning stock biomass, black
lines are total biomass, and grey dashed lines are commercial trawl fishery 
exploitable biomass. Catch bars show realised catch in grey for the whole
simulation period, and in the projection period TACs set by the harvest control
rule are shown as hollow black rectangles over the grey catch bars."

scaledIndicesCap <- "Assessment model fits to biomass indices in the first
year of the projections. Indices are shown as data points scaled by the
AM estimates of catchability. Red lines are spawning stock biomass, black
lines are total biomass, and grey dashed lines are commercial trawl fishery 
exploitable biomass. Grey bars show catch in the historical period."

AMidxResidsCap <- "Standardised residuals of assessment model fits
to biomass indices. Point colours correspond to fleets, while point
shapes are stock areas."

JabbaSelModelCap <- "Ratios between spawning biomass and vulnerable
biomass ($y$ axis) at a given spawning biomass depletion ($x$ axis) 
for each fleet (colours)."

```


# Simulation envelopes

## Spawning Biomass

```{r, plotTulipBtCt, echo = FALSE, message = FALSE, fig.cap = SBsptCaption }
if( any(nGoodReps_sp >= 1) )
  plotTulipBt( obj = blob, dep = TRUE, Ct = TRUE )
```

## TAC utilisation

```{r, plotTulipTACu, echo = FALSE, message = FALSE, fig.cap = TACuCaption }
if( any(nGoodReps_sp >= 1) )
  plotTulipTACu( obj = blob, nTrace = 3 )
```

## Fishing mortality

```{r, plotTulipF, echo = FALSE, message = FALSE, fig.cap = EffTulipCaption }
if( any(nGoodReps_sp >= 1) )
  plotTulipF( obj = blob )
```


## Effort allocation

```{r, plotTulipEffort, echo = FALSE, message = FALSE, fig.cap = FTulipCaption }
if( any(nGoodReps_sp >= 1) )
  plotTulipEffort_p( obj = blob )
```

# Example replicates

## Retrospective biomass

```{r, plotRetroSB, echo = FALSE, message = FALSE, fig.cap = retroSBCaption }
plotRetroSBagg(obj = blob, iRep = randReplicate)
```

## Model fits in first year
```{r, plotScaledIndices, echo = FALSE, message = FALSE, fig.cap = scaledIndicesCap }
if(!blob$ctlList$ctl$omni)
  plotScaledIndices(  obj = blob,
                      iRep = randReplicate,
                      t = tMP )
```


```{r, plotAMresids, echo = FALSE, message = FALSE, fig.cap = AMidxResidsCap }
if(!blob$ctlList$ctl$omni)
  plotAMIdxResids(  obj = blob,
                    iRep = randReplicate,
                    t = tMP )
```


```{r, plotJabbaModel, echo = FALSE, message = FALSE, fig.cap = JabbaSelModelCap }
if( !is.null(blob$ctlList$mp$assess$spSkewYieldCurves) )
  plotEBSBratio(  obj = blob )
```



# Performance

## Stats table

```{r, simPerfStats, echo = FALSE }

statTable <- .simPerfStats( obj = blob )

kable(  statTable, escape = FALSE, 
        caption = "Performance statistics for this simulation.", booktabs = T,
        align = rep("c",ncol(statTable))) %>%
  kable_styling( latex_options = c("striped", "scale_down","hold_position"),
                 bootstrap_options = c("striped", "hover"))

```



```{r, plotConvergence, echo = FALSE, message = FALSE, fig.cap = convStatsCaption, results = "as-is" }
if(   !(blob$ctlList$ctl$omni | blob$ctlList$ctl$perfConF)  & 
    ( !blob$ctlList$mp$assess$method %in% c("idxBased","PerfectInfo" ) ) )
{

  cat(paste("## ", "Convergence diagnostics\n",sep = ""))

  if( any(nGoodReps_sp > 0) )
    plotConvStats( obj = blob )
  else
    cat("**NO CONVERGENT REPLICATES**\n")
}
```

```{r, omniTitle, echo = FALSE, message = FALSE, results = "asis" }
if(blob$ctlList$ctl$omni)
{
  childDoc <- knitr::knit_child(here::here("docs","reports","omniSimReportChild.Rmd"),options = list(results = "asis"),quiet = TRUE)

  cat(childDoc)
}

```



