\clearpage

# (APPENDIX) Appendices {-}

# Appendix A: Fits to compositional data


```{r ageFitAvg, echo = FALSE, fig.cap = "ageFitAvgDover HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 1, pIdx = 1,
                            sex = "female",
                            comps = "age"  )
```

\clearpage

```{r ageFitAvg2, echo = FALSE, fig.cap = "ageFitAvgEnglish HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 2, pIdx = 1,
                            sex = "female",
                            comps = "age" )
```

\clearpage

```{r ageFitAvg3, echo = FALSE, fig.cap = "ageFitAvg Rock HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 3, pIdx = 1,
                            sex = "female",
                            comps = "age" )
```

# Appendix B: DER complex time-varying inverse demand curves

Ex-vessel unit prices ($/kg) for each DER complex species $s$ were 
assumed to follow an inverse demand curve
\begin{equation}
v_{s}(\sum_{p} C_{s,p}) = v^*_{s} \left( \frac{\sum_p C_{s,p}}{ \sum_p MSY_{SS,s,p}}  \right) ^{1/\lambda_s},
\end{equation}
where $v_s$ was the ex-vessel unit price, $C_{s,p}$ was the catch of
species $s$ in area $p$, $v^*_s$ was the reference ex-vessel unit price of 
species $s$, which was realised when coast-wide catch $\sum_p C_{s,p}$ 
(quantity supplied) was equal to the sum of area-specific maximum 
sustainable yield $\sum_p MSY_{s,p}$, and $\lambda_s$ was the constant 
elasticity of demand reducing price with quantity supplied.

To fit to the ex-vessel price data from 2006 - 2016, we included a 
time-varying reference price $v^*_{s,t}$, which
