\clearpage

# (APPENDIX) Appendices {-}

# Appendix A: Fits to compositional data


```{r ageFitAvg, echo = FALSE, fig.cap = "ageFitAvgDover HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 1, pIdx = 1,
                            sex = "female",
                            comps = "age"  )
```

\clearpage

```{r ageFitAvg2, echo = FALSE, fig.cap = "ageFitAvgEnglish HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 2, pIdx = 1,
                            sex = "female",
                            comps = "age" )
```

\clearpage

```{r ageFitAvg3, echo = FALSE, fig.cap = "ageFitAvg Rock HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 3, pIdx = 1,
                            sex = "female",
                            comps = "age" )
```

# Appendix B: DER complex time-varying inverse demand curves

We assumed that ex-vessel unit prices ($/kg) for each DER complex 
species $s$ followed a time-varying inverse demand curve
\begin{equation}
v_{s,t}(\sum_{p} C_{s,p,t}) = v^*_{s,t} \left( \frac{\sum_p C_{s,p,t}}{ \sum_p MSY_{SS,s,p}}  \right) ^{1/\lambda_s},
\end{equation}
where $v_{s,t}$ was the ex-vessel unit price, $C_{s,p,t}$ was catch,
$v^*_{s,t}$ was the reference ex-vessel unit price realised when coast-wide 
catch $\sum_p C_{s,p,t}$ (quantity supplied) was equal to the sum of area-specific maximum 
sustainable yield $\sum_p MSY_{s,p}$, and $\lambda_s$ was the constant 
elasticity of demand reducing price with quantity supplied, with indices for
species $s$, area $p$, and year $t$. The reference price $v^*_{s,t}$ varied 
via a simple random walk in logit-space
\begin{align}
\logit \upsilon^*_{s,t} &= \logit \upsilon^*_{s,t-1} + \delta_{s,t}, \\
v^*_{s,t} &= 0.5 \cdot P^{min}_{s} + \frac{\mathcal{P}^{max}_s - \mathcal{P}^{min}_s}{1 + exp(-\logit \upsilon^*{s,t})}
\end{align}
where $\upsilon^*_{s,t}$ was the unbounded logit-scale parameter transformed
to the reference price $v^*_{s,t}$, $\delta_{s,t}$ was a normal deviation, 
and $v^*_{s,t}$ was bounded between half of $P^{\min}_s$ and twice
$P^{\max}_s$, the lowest and highest observed prices, respectively, of 
species $s$ between 2006 and 2016.

Elasticity of demand $\lambda_s$, and the covariance of the random walk 
deviations $\delta_{s,t}$ were estimated by fitting the time-varying
inverse demand curve to catch and price data from 2006 - 2016. Leading
parameters $\lambda_s$, $\delta_{s,t}$, and the 2016 reference price
$v^*_{s,2016}$ were estimated via Newton-Rhapson optimisation of the
objective function
\begin{equation}
\mathcal{O} = \frac{33}{2} \left( \frac{\left( \log P_{s,t} - \log v_{s,t} \right)^2}{33} + 1 \right) + \sum_{s,t} \delta_{s,t}^2,
\end{equation} 
where $P_{s,t}$ is the observed ex-vessel prices for DER complex species
from 2006 to 2016, and $v_{s,t}$ are the expected prices given by Equation 
REF above. Random walk deviations $\delta_{s,t}$ were allowed to vary with 
a standard deviation of 1.0, which allowed the residual error 
$\log P_{s,t} - \log v_{s,t}$ to approach zero, solving for the random walk 
jumps required to produce the observed prices $P_{s,t}$ at the observed 
quantities supplied $C_{s,p,t}$ given a constant elasticity of 
demand $\lambda_s$. Covariance of $\delta_{s,t}$ was estimated directly from
the optimised solution.
