\clearpage

# (APPENDIX) Appendices {-}

# Appendix A: DER complex demand analysis

\clearpage
\setcounter{table}{0}  
\renewcommand{\thetable}{A\arabic{table}} 
\setcounter{figure}{0} 
\renewcommand{\thefigure}{A\arabic{figure}}

The unit price $v_s$ ($/kg) of each DER complex species $s$ is assumed to 
follow a downward sloping demand curve for total catch $C_s$ (quantity 
demanded) with a constant own-price elasticity of demand. Demand 
curve identifiability was a problem, given the low sample size (11 years) 
of economic data and the sometimes positive relationship between BC catch 
and the unit price, indicating either demand or supply shifts that created
correlation between explanatory variables (i.e., price) and the
residual in the quantity demanded, also known as endogeneity
[@angrist2008mostly]. 

DER complex demand curves are fit to landings, ex-vessel prices, and
BC household income per capita. Average ex-vessel unit price ($/kg) data for 
the DER complex is obtained from dockside fish-slips for the BC trawl 
fishery from 2006 - 2016, and calculated as total ex-vessel revenues 
divided by total landings ^[Department of Fisheries and Oceans (2019). 
Commercial Pacific Landings. Unpublished data Table.  Available 
from Pacific.CatchStats@dfo-mpo.gc.ca]. All ex-vessel prices are specific 
to the bottom trawl fishery except for English Sole in 2016, which is an 
outlier with a trawl ex-vessel price almost three times the 2006 - 2016 
average, and is therefore replaced with the 2016 ex-vessel price for 
English sole averaged across all available gear types. All prices are
then adjusted to 2016 dollars by using the annual average consumer price
index (CPI) from Statistics Canada ^[Table 18-10-0256-01  Consumer Price 
Index (CPI) statistics, measures of core inflation and other related 
statistics - Bank of Canada definitions, 
https://doi.org/10.25318/1810025601-eng]. 
BC household income per capita data (Table A1) is also obtained from 
Statistics Canada ^[Table 36-10-0229-01, Long-run provincial and 
territorial data, https://doi.org/10.25318/3610022901-eng].

Annual catches of Dover and English soles on the US west coast (i.e., 
Washington, Oregon, and California, but not Alaska) are added to the BC 
catch (Table A1) [@wetzel2019catch-update-fo; @cope2013data]. The BC 
groundfish trawl fishery is known coloquially as an "I-5 Fishery" 
(pers comm. Chris Sporer), because, in addition to local BC customers, 
fish caught in BC are sold to restaurants and retailers along the US west 
coast via the I-5 highway. Similarly, fish caught on the US west coast 
are sold in BC. Therefore, the market price for BC trawl catch is dependent 
on the catch from the US west coast, and demand models fit to catch and 
price data do not match economic assumptions about market dynamics without
the exogenous catch data (i.e., demand curves are upward sloping). Rock 
sole catch is not assessed on the west coast because there are not 
significant populations or catches. Further, Rock sole demand curves 
are downward sloping without the exogenous catch. US west coast catch 
data are unavailable after 2013 for English sole as there has not been 
an assessment since that time, so West coast US English sole catch for 
2013 - 2016 is assumed to be constant at the 2013 level. 

```{r exogCatchTable, echo = FALSE}
UScatch_st <- priceModel$UScatch_st
GDPperCap_t <- priceModel$bcIncome_t

econDataTable <- array(NA, dim = c(11,4))
colnames(econDataTable) <- c("Year","Dover","English","GDPpc")
econDataTable <- as.data.frame(econDataTable)

econDataTable$Year <- 2006:2016
econDataTable$Dover <- UScatch_st[1,]
econDataTable$English <- UScatch_st[2,]
econDataTable$GDPpc <- GDPperCap_t

exogCatchCap <- "US catches and BC household income per capita 
data used for estimating the DER complex inverse demand curves."

csasdown::csas_table( econDataTable, escape = FALSE,
                      booktabs = TRUE, font_size = 10,
                      format = kableFormat,
                      caption = exogCatchCap,
                      align = c("l","l","l","l")) %>%
  kable_styling(latex_options = c("striped", "hold_position","scale_down"),
                bootstrap_options = c("striped", "hover")) 




```

A 2-stage least squares (2SLS) regression was used to reduce endogeneity,
predicting the unit price using instrumental variables 
[@angrist2001instrumental]. The instrument was the unit cost of supplying 
catch of each species, estimated via assumed fuel costs 
\begin{equation}
w_{s,t} = \frac{\sum_{p} E_p \cdot c_p}{\sum_p C_{s,p}},
\end{equation}.
where $c_p$ is derived in the Section 2. The first stage 
then regresses the observed ex-vessel log-price 
$v_{s,t}$ for species $s$ in year $t$ year on the log-cost of supply 
\begin{equation}
\log v_{s,t} = \alpha_{0,s} + \alpha_{1,s} \log w_{s,t},
\end{equation}
and uses the resulting coefficents $\alpha_{i,s}$ to predict a
unit price $\hat{v}_{s,t}$ with less (or no) endogeneity.
The predicted price $\hat{v}_{s,t}$ is then used as an explanatory
variable in the second stage regression for the demand curve
\begin{equation}
\log C_{s,t} = \beta_{0,s} + \lambda_s \log \hat{v}_{s,t} + \beta_{1,s} y_t,
\end{equation}
where $C_{s,t}$ is the US west coast and BC catch in year $t$,
$\lambda_s$ is the own price elasticity of demand for species $s$
[@cheng1988demand], and $y_t$ is the British Columbia household income 
per capita in year $t$. When modeling an inverse demand curve, with price 
as the response variable, the quantity $\frac{1}{\lambda_s}$ is called 
price flexibility [@jaffry1999long]. We also fit models with cross-price 
elasticity of demand, but none of the coefficients for substitution
between species are significant so we do not report them here or
use them in projections.

Demand relationships from the 2SLS fit the data well, and are suitable for 
projections in closed-loop simulations. Coefficients from price 
regressions on cost of fishing instruments are not significant
at the 0.05 level for any species (Table A1), but do reasonably
well at reducing endogeneity in the price data (Figure 2, main body,
compare open points to closed point). Despite the low explanatory power
of the fuel cost instrument, IV estimates of unit prices showed
that all three species have elastic demand (Table A2), which is
within range of previous demand analyses of flatfish [@asche2007studies]. 
English and Rock sole demand was more elastic than Dover sole
demand, which was only slightly elastic (Table A2) and not significant at 
the $p = 0.1$ level ($p = 0.101$). The higher probability of a spurious 
estimate for Dover sole is expected, as the catch and price data show a 
fairly flat relationship, even after the IV regression, that would fit 
equally well to many different price elasticities of demand (Fig 2, main 
body). However, the inverse demand relationship is sufficient for the 
purpose of simulating realistic demand in model projections, as the curve 
does not contradict the data, and the demand is downward sloping 
[@pascoe2018offsetting]. Further, $p$ values are continuous, and
$p = 0.101$ is a low probability of a spurious effect, given the 
uninformative data. All species have a negative
income elasticity parameter $\beta_1$, indicating that the price will 
decrease for a given quantity demanded (catch) as household incomes 
increase. Such a reduction in demand from higher incomes may implies 
that DER complex flatfishes are an inferior good [@dey2011multistage], 
which means that families with more disposable income will switch to 
more expensive sources of protein, such as higher value fish or beef, 
rather than the inexpensive flatfishes of the DER complex.

```{r invDemCurveTables, echo = FALSE}
priceIVreg <- priceModel$priceInstrument_s

invDemCurves  <- priceModel$invDemCurvesOwnElast_s
demCurves     <- priceModel$demCurvesOwnElast_s

invDemTable <- array(NA, dim = c(3,7))
dimnames(invDemTable)[[2]] <- c(  "Species",
                                  "alpha0",
                                  "alpha1",
                                  "beta0",
                                  "priceFlex",
                                  "beta1",
                                  "lambda")
invDemTable <- as.data.frame(invDemTable)


demTable <- array(NA, dim = c(3,4))
dimnames(demTable)[[2]] <- c( "Species",
                              "beta0",
                              "lambda",
                              "beta1")
demTable <- as.data.frame(demTable)
demTable$Species <- c("Dover","English","Rock")

invDemTable$Species <- c("Dover","English","Rock")


invDemTable[1,2:3] <- round(coef(priceIVreg[[1]]),3)
invDemTable[2,2:3] <- round(coef(priceIVreg[[2]]),3)
invDemTable[3,2:3] <- round(coef(priceIVreg[[3]]),3)


invDemTable[1,4:6] <- round(coef(invDemCurves[[1]]),3)
invDemTable[2,4:6] <- round(coef(invDemCurves[[2]]),3)
invDemTable[3,4:6] <- round(coef(invDemCurves[[3]]),3)

demTable[1,2:4] <- round(coef(demCurves[[1]]),3)
demTable[2,2:4] <- round(coef(demCurves[[2]]),3)
demTable[3,2:4] <- round(coef(demCurves[[3]]),3)

invDemTable <-  invDemTable %>%
                  mutate(lambda = round(1/priceFlex,3))

invDemTable[2,4:6] <- paste0(invDemTable[2,4:6],"*")
invDemTable[3,4:6] <- paste0(invDemTable[3,4:6],"*")

demTable[1,c(2,4)] <- paste0(demTable[1,c(2,4)],"*")
demTable[2,2:4] <- paste0(demTable[2,2:4],"*")
demTable[3,2:4] <- paste0(demTable[3,2:4],"*")


invDemCap <- "Two-stage least-squares regression results when
modeling inverse demand (price is the response variable). An asterisk 
denotes that the parameters were significant at the $p = 0.1$ level."

# demCap <- "Two-stage least-squares regression results when
# modeling demand (catch/quant supplied is the response variable). An 
# asterisk denotes that the parameters were significant at the p = 0.1 level."



csasdown::csas_table( invDemTable, escape = FALSE,
                      booktabs = TRUE, font_size = 10,
                      format = kableFormat,
                      caption = invDemCap,
                      align = rep("l",5)) %>%
  kable_styling(latex_options = c("striped", "hold_position","scale_down"),
                bootstrap_options = c("striped", "hover")) %>%
  add_header_above( header = c( " " = 1,
                                "Price IV model" = 2,
                                "Inv demand" = 3,
                                " " = 1),
                    bold = TRUE)

# csasdown::csas_table( demTable, escape = FALSE,
#                     booktabs = TRUE, font_size = 10,
#                     format = kable_format,
#                     caption = demCap,
#                     align = rep("l",5)) %>%
# kable_styling(latex_options = c("striped", "hold_position","scale_down"),
#               bootstrap_options = c("striped", "hover")) %>%
# add_header_above( header = c( " " = 1,
#                               "Demand" = 3),
#                   bold = TRUE)



```

To simulate price as a function of catch (i.e., the inverse demand 
relationship) in model projections, two simplifying assumptions
are made. First, US West Coast Dover and English sole catches are 
assumed to be exogenous and fixed at the average catch for the 2006 - 
2016 time period, and second, growth in median BC household income is
assumed to be at the fixed rate of 3.9\% per year 
^[https://www2.gov.bc.ca/assets/gov/british-columbians-our-governments/government-finances/financial-economic-review/financial-economic-review-2020.pdf].

For sensitivity analyses, inverse demand curves are refit to the
price instrument and household incomes assuming own-price elasticity
was infinite (i.e., $\frac{1}{\lambda_s} = 0$ for all species). When
price-flexibility is removed from the inverse demand curve, the parameters
are very different. Dover and English soles have no significant parameters
($0.4 < p < 0.65$), while Rock sole's inverse demand curve has 
significant coefficients at the $p = 0.1$ level. Further, while Dover and
English soles have a reduction in price with household incomes, as above,
Rock sole's relationship with income is reversed, showing demand will
increase with household income. This is not unexpected, as Rock sole has the 
smallest magnitude $\beta_1$ coefficient in the finite elasticity case,
and is sometimes considered a more desirable eating fish. 


```{r infPEDcurveTables, echo = FALSE}
invDemCurves  <- priceModel$invDemCurvesInfPED_s

invDemTable <- array(NA, dim = c(3,3))
dimnames(invDemTable)[[2]] <- c(  "Species",
                                  "beta0",
                                  "beta1" )
invDemTable <- as.data.frame(invDemTable)

invDemTable$Species <- c("Dover","English","Rock")


invDemTable[1,2:3] <- round(coef(invDemCurves[[1]]),3)
invDemTable[2,2:3] <- round(coef(invDemCurves[[2]]),3)
invDemTable[3,2:3] <- round(coef(invDemCurves[[3]]),3)


invDemTable[3,2:3] <- paste0(invDemTable[3,2:3],"*")


invDemCap <- "Two-stage least-squares regression results when
modeling inverse demand assuming own-price elasticity is infinite. 
An asterisk denotes that the parameters were significant at 
the $p = 0.1$ level."

# demCap <- "Two-stage least-squares regression results when
# modeling demand (catch/quant supplied is the response variable). An 
# asterisk denotes that the parameters were significant at the p = 0.1 level."



csasdown::csas_table( invDemTable, escape = FALSE,
                      booktabs = TRUE, font_size = 10,
                      format = kableFormat,
                      caption = invDemCap,
                      align = rep("l",5)) %>%
  kable_styling(latex_options = c("striped", "hold_position","scale_down"),
                bootstrap_options = c("striped", "hover")) %>%
  add_header_above( header = c( " " = 1,
                                "Inv demand" = 2),
                    bold = TRUE)

  # csasdown::csas_table( demTable, escape = FALSE,
  #                     booktabs = TRUE, font_size = 10,
  #                     format = kable_format,
  #                     caption = demCap,
  #                     align = rep("l",5)) %>%
  # kable_styling(latex_options = c("striped", "hold_position","scale_down"),
  #               bootstrap_options = c("striped", "hover")) %>%
  # add_header_above( header = c( " " = 1,
  #                               "Demand" = 3),
  #                   bold = TRUE)



```

<!-- \begin{equation} 
v_{s}(\sum_{p} C_{s,p}) = v^*_{s} \left( \frac{\sum_p C_{s,p}}{ \sum_p MSY_{SS,s,p}}  \right) ^{1/\lambda_s}
\end{equation}
where $v^*{s}$ was the 2016 reference price of species $s$ when catch 
was the sum of single-species MSY for each area, and $\lambda_s < 0$ is 
the price elasticity of demand [@varian1992microeconomic]. The price 
elasticity of demand $\lambda_s$ and 2016 reference price $v^*_s$ were 
found by fitting a time-varying inverse demand curve to average ex-vessel 
prices and catch data between 2006 and 2016 (see Appendix B). Modeling 
price as a decreasing function of quantity supplied captured the incentive 
of harvesters to reduce catch and keep prices higher through artificial 
scarcity, which results in a transfer of benefits (surplus) from consumers 
to producers [@pascoe2018offsetting]. 

We assumed that ex-vessel unit prices ($/kg) for each DER complex 
species $s$ followed a time-varying inverse demand curve
\begin{equation}
v_{s,t}(\sum_{p} C_{s,p,t}) = v^*_{s,t} \left( \frac{\sum_p C_{s,p,t}}{ \sum_p MSY_{SS,s,p}}  \right) ^{1/\lambda_s},
\end{equation}
where $v_{s,t}$ was the ex-vessel unit price, $C_{s,p,t}$ was catch,
$v^*_{s,t}$ was the reference ex-vessel unit price realised when coast-wide 
catch $\sum_p C_{s,p,t}$ (quantity supplied) was equal to the sum of area-specific maximum 
sustainable yield $\sum_p MSY_{s,p}$, and $\lambda_s$ was the constant 
elasticity of demand reducing price with quantity supplied, with indices for
species $s$, area $p$, and year $t$. The reference price $v^*_{s,t}$ varied 
via a simple random walk in logit-space
\begin{align}
\logit \upsilon_{s,t} &= \logit \upsilon_{s,t-1} + \delta_{s,t}, \\
v^*_{s,t} &= 0.5 \cdot P^{min}_{s} + \frac{\mathcal{P}^{max}_s - \mathcal{P}^{min}_s}{1 + exp(-\logit \upsilon{s,t})}
\end{align}
where $\upsilon_{s,t}$ was the unbounded logit-scale parameter transformed
to the reference price $v^*_{s,t}$, $\delta_{s,t}$ was a normal deviation, 
and $v^*_{s,t}$ was bounded between half of $P^{\min}_s$ and twice
$P^{\max}_s$, the lowest and highest observed prices, respectively, of 
species $s$ between 2006 and 2016.

Price elasticity of demand $\lambda_s$, and the covariance of the random walk 
deviations $\delta_{s,t}$ were estimated by fitting the time-varying
inverse demand curve to catch and price data from 2006 - 2016. Leading
parameters $\lambda_s$, $\delta_{s,t}$, and the 2016 reference price
$v^*_{s,2016}$ were estimated via Newton-Rhapson optimisation of the
objective function
\begin{equation}
\mathcal{O} = \frac{33}{2} \left( \frac{\left( \log P_{s,t} - \log v_{s,t} \right)^2}{33} + 1 \right) + \sum_{s,t} \delta_{s,t}^2,
\end{equation} 
where $P_{s,t}$ is the observed ex-vessel prices for DER complex species
from 2006 to 2016, and $v_{s,t}$ are the expected prices given by Equation 
REF above. Random walk deviations $\delta_{s,t}$ were allowed to vary with 
a standard deviation of 1.0, which allowed the residual error 
$\log P_{s,t} - \log v_{s,t}$ to approach zero, solving for the random walk 
jumps required to produce the observed prices $P_{s,t}$ at the observed 
quantities supplied $C_{s,p,t}$ given a constant elasticity of 
demand $\lambda_s$. Covariance $\Sigma$ of the random walk jumps
$\delta_{s,t}$ was derived from the estimated jumps themselves, rather
than within the model.
 -->



