\clearpage

# (APPENDIX) Appendices {-}

# Appendix A: DER complex demand analysis

\clearpage
\setcounter{table}{0}  
\renewcommand{\thetable}{A\arabic{table}} 
\setcounter{figure}{0} 
\renewcommand{\thefigure}{A\arabic{figure}}

The unit price $v_s$ ($/kg) of each DER complex species $s$ is assumed to 
follow a downward sloping demand curve for total catch $C_s$ (quantity 
demanded) with a constant own-price elasticity of demand. Demand 
curve identifiability was a problem, given the low sample size (11 years) 
of economic data and the sometimes positive relationship between BC catch 
and the unit price, indicating either demand or supply shifts that created
correlation between explanatory variables (i.e., price) and the
residual in the quantity demanded, also known as endogeneity
[@angrist2008mostly]. 

DER complex demand curves are fit to landings, ex-vessel prices, and
BC household income per capita. Average ex-vessel unit price ($/kg) data for 
the DER complex is obtained from dockside fish-slips for the BC trawl 
fishery from 2006 - 2016, and calculated as total ex-vessel revenues 
divided by total landings ^[Department of Fisheries and Oceans (2019). 
Commercial Pacific Landings. Unpublished data Table.  Available 
from Pacific.CatchStats@dfo-mpo.gc.ca]. All ex-vessel prices are specific 
to the bottom trawl fishery except for English Sole in 2016, which is an 
outlier with a trawl ex-vessel price almost three times the 2006 - 2016 
average, and is therefore replaced with the 2016 ex-vessel price for 
English sole averaged across all available gear types. All prices are
then adjusted to 2016 dollars by using the annual average consumer price
index (CPI) from Statistics Canada ^[Table 18-10-0256-01  Consumer Price 
Index (CPI) statistics, measures of core inflation and other related 
statistics - Bank of Canada definitions, 
https://doi.org/10.25318/1810025601-eng]. 
BC household income per capita data (Table A1) is also obtained from 
Statistics Canada ^[Table 36-10-0229-01, Long-run provincial and 
territorial data, https://doi.org/10.25318/3610022901-eng].

Annual catches of Dover and English soles on the US west coast (i.e., 
Washington, Oregon, and California, but not Alaska) are added to the BC 
catch (Table A1) [@wetzel2019catch-update-fo; @cope2013data]. The BC 
groundfish trawl fishery is known coloquially as an "I-5 Fishery" 
(pers comm. Chris Sporer), because, in addition to local BC customers, 
fish caught in BC are sold to restaurants and retailers along the US west 
coast via the I-5 highway. Similarly, fish caught on the US west coast 
are sold in BC. Therefore, the market price for BC trawl catch is dependent 
on the catch from the US west coast, and demand models fit to catch and 
price data do not match economic assumptions about market dynamics without
the exogenous catch data (i.e., demand curves are upward sloping). Rock 
sole catch is not assessed on the west coast because there are not 
significant populations or catches. Further, Rock sole demand curves 
are downward sloping without the exogenous catch. US west coast catch 
data are unavailable after 2013 for English sole as there has not been 
an assessment since that time, so West coast US English sole catch for 
2013 - 2016 is assumed to be constant at the 2013 level. 

```{r exogCatchTable, echo = FALSE}
UScatch_st <- priceModel$UScatch_st
GDPperCap_t <- priceModel$bcIncome_t

econDataTable <- array(NA, dim = c(11,4))
colnames(econDataTable) <- c("Year","Dover","English","GDPpc")
econDataTable <- as.data.frame(econDataTable)

econDataTable$Year <- 2006:2016
econDataTable$Dover <- UScatch_st[1,]
econDataTable$English <- UScatch_st[2,]
econDataTable$GDPpc <- GDPperCap_t

exogCatchCap <- "US catches and BC household income per capita 
data used for estimating the DER complex inverse demand curves."

csasdown::csas_table( econDataTable, escape = FALSE,
                      booktabs = TRUE, font_size = 10,
                      format = kableFormat,
                      caption = exogCatchCap,
                      align = c("l","l","l","l")) %>%
  kable_styling(latex_options = c("striped", "hold_position","scale_down"),
                bootstrap_options = c("striped", "hover")) 




```

A 2-stage least squares (2SLS) regression was used to reduce endogeneity,
predicting the unit price using instrumental variables 
[@angrist2001instrumental]. The instrument was the unit cost of supplying 
catch of each species, estimated via assumed fuel costs 
\begin{equation}
w_{s,t} = \frac{\sum_{p} E_p \cdot c_p}{\sum_p C_{s,p}},
\end{equation}.
where $c_p$ is derived in the Section 2. The first stage 
then regresses the observed ex-vessel log-price 
$v_{s,t}$ for species $s$ in year $t$ year on the log-cost of supply 
\begin{equation}
\log v_{s,t} = \alpha_{0,s} + \alpha_{1,s} \log w_{s,t},
\end{equation}
and uses the resulting coefficents $\alpha_{i,s}$ to predict a
unit price $\hat{v}_{s,t}$ with less (or no) endogeneity.
The predicted price $\hat{v}_{s,t}$ is then used as an explanatory
variable in the second stage regression for the demand curve
\begin{equation}
\log C_{s,t} = \beta_{0,s} + \lambda_s \log \hat{v}_{s,t} + \beta_{1,s} y_t,
\end{equation}
where $C_{s,t}$ is the US west coast and BC catch in year $t$,
$\lambda_s$ is the own-price elasticity for species $s$
[@cheng1988demand], $\beta_{1,s}$ is the income elasticity, and $y_t$ 
is the British Columbia household income per capita in year $t$. When 
modeling an inverse demand curve, with price 
as the response variable, the quantity $\frac{1}{\lambda_s}$ is called 
price flexibility [@jaffry1999long]. We also fit models with cross-price 
elasticity of demand, but none of the coefficients for substitution
between species are significant so we do not report them here or
use them in projections.

Demand relationships from the 2SLS fit the data well, and are suitable for 
projections in closed-loop simulations. Coefficients from price 
regressions on cost of fishing instruments are not significant
at the 0.05 level for any species (Table A1), but do reasonably
well at reducing endogeneity in the price data (Figure 2, main body,
compare open points to closed point). Despite the low explanatory power
of the fuel cost instrument, IV estimates of unit prices showed
that all three species have elastic demand (Table A2), which is
within range of previous demand analyses of flatfish [@asche2007studies]. 
English and Rock sole demand was more elastic than Dover sole
demand, which was only slightly elastic (Table A2) and not significant at 
the $p = 0.1$ level ($p = 0.101$). The higher probability of a spurious 
estimate for Dover sole is expected, as the catch and price data show a 
fairly flat relationship, even after the IV regression, that would fit 
equally well to many different price elasticities of demand (Fig 2, main 
body). However, the inverse demand relationship is sufficient for the 
purpose of simulating realistic demand in model projections, as the curve 
does not contradict the data, and the demand is downward sloping 
[@pascoe2018offsetting]. Further, $p$ values are continuous, and
$p = 0.101$ is a low probability of a spurious effect, given the 
uninformative data. All species have a negative
income elasticity parameter $\beta_1$, indicating that they are all
inferior goods [@dey2011multistage], which means that families with 
more disposable income will switch to more expensive sources of protein, 
such as higher value fish or beef, rather than the inexpensive 
flatfishes of the DER complex.

```{r invDemCurveTables, echo = FALSE}
priceIVreg <- priceModel$priceInstrument_s

invDemCurves  <- priceModel$invDemCurvesOwnElast_s
demCurves     <- priceModel$demCurvesOwnElast_s

invDemTable <- array(NA, dim = c(3,7))
dimnames(invDemTable)[[2]] <- c(  "Species",
                                  "alpha0",
                                  "alpha1",
                                  "beta0",
                                  "priceFlex",
                                  "beta1",
                                  "lambda")
invDemTable <- as.data.frame(invDemTable)


demTable <- array(NA, dim = c(3,4))
dimnames(demTable)[[2]] <- c( "Species",
                              "beta0",
                              "lambda",
                              "beta1")
demTable <- as.data.frame(demTable)
demTable$Species <- c("Dover","English","Rock")

invDemTable$Species <- c("Dover","English","Rock")


invDemTable[1,2:3] <- round(coef(priceIVreg[[1]]),3)
invDemTable[2,2:3] <- round(coef(priceIVreg[[2]]),3)
invDemTable[3,2:3] <- round(coef(priceIVreg[[3]]),3)


invDemTable[1,4:6] <- round(coef(invDemCurves[[1]]),3)
invDemTable[2,4:6] <- round(coef(invDemCurves[[2]]),3)
invDemTable[3,4:6] <- round(coef(invDemCurves[[3]]),3)

demTable[1,2:4] <- round(coef(demCurves[[1]]),3)
demTable[2,2:4] <- round(coef(demCurves[[2]]),3)
demTable[3,2:4] <- round(coef(demCurves[[3]]),3)

invDemTable <-  invDemTable %>%
                  mutate(lambda = round(1/priceFlex,3))

invDemTable[2,4:6] <- paste0(invDemTable[2,4:6],"*")
invDemTable[3,4:6] <- paste0(invDemTable[3,4:6],"*")

demTable[1,c(2,4)] <- paste0(demTable[1,c(2,4)],"*")
demTable[2,2:4] <- paste0(demTable[2,2:4],"*")
demTable[3,2:4] <- paste0(demTable[3,2:4],"*")


invDemCap <- "Two-stage least-squares regression results when
modeling inverse demand (price is the response variable). An asterisk 
denotes that the parameters were significant at the $p = 0.1$ level."

# demCap <- "Two-stage least-squares regression results when
# modeling demand (catch/quant supplied is the response variable). An 
# asterisk denotes that the parameters were significant at the p = 0.1 level."



csasdown::csas_table( invDemTable, escape = FALSE,
                      booktabs = TRUE, font_size = 10,
                      format = kableFormat,
                      caption = invDemCap,
                      align = rep("l",5)) %>%
  kable_styling(latex_options = c("striped", "hold_position","scale_down"),
                bootstrap_options = c("striped", "hover")) %>%
  add_header_above( header = c( " " = 1,
                                "Price IV model" = 2,
                                "Inv demand" = 3,
                                " " = 1),
                    bold = TRUE)

# csasdown::csas_table( demTable, escape = FALSE,
#                     booktabs = TRUE, font_size = 10,
#                     format = kable_format,
#                     caption = demCap,
#                     align = rep("l",5)) %>%
# kable_styling(latex_options = c("striped", "hold_position","scale_down"),
#               bootstrap_options = c("striped", "hover")) %>%
# add_header_above( header = c( " " = 1,
#                               "Demand" = 3),
#                   bold = TRUE)



```

To simulate price as a function of catch (i.e., the inverse demand 
relationship) in model projections, two simplifying assumptions
are made. First, US West Coast Dover and English sole catches are 
assumed to be exogenous and fixed at the average catch for the 2006 - 
2016 time period, and second, growth in median BC household income is
assumed to be at the fixed rate of 3.9\% per year 
^[https://www2.gov.bc.ca/assets/gov/british-columbians-our-governments/government-finances/financial-economic-review/financial-economic-review-2020.pdf].

For sensitivity analyses, inverse demand curves are refit to the
price instrument and household incomes assuming own-price elasticity
was infinite (i.e., $\frac{1}{\lambda_s} = 0$ for all species). When
price-flexibility is removed from the inverse demand curve, the parameters
are very different. Dover and English soles have no significant parameters
($0.4 < p < 0.65$), while Rock sole's inverse demand curve has 
significant coefficients at the $p = 0.1$ level. Further, while Dover and
English soles have a reduction in price with household incomes, as above,
Rock sole's relationship with income is reversed, showing that it
is no longer an inferior good and demand will increase with household 
income. This indicates that own-price elasticity and income elasticity
are confounded, but is not wholly unexpected, as Rock sole has the 
smallest magnitude $\beta_1$ coefficient in the finite elasticity case,
and is sometimes considered a more desirable eating fish. 


```{r infPEDcurveTables, echo = FALSE}
invDemCurves  <- priceModel$invDemCurvesInfPED_s

invDemTable <- array(NA, dim = c(3,3))
dimnames(invDemTable)[[2]] <- c(  "Species",
                                  "beta0",
                                  "beta1" )
invDemTable <- as.data.frame(invDemTable)

invDemTable$Species <- c("Dover","English","Rock")


invDemTable[1,2:3] <- round(coef(invDemCurves[[1]]),3)
invDemTable[2,2:3] <- round(coef(invDemCurves[[2]]),3)
invDemTable[3,2:3] <- round(coef(invDemCurves[[3]]),3)


invDemTable[3,2:3] <- paste0(invDemTable[3,2:3],"*")


invDemCap <- "Two-stage least-squares regression results when
modeling inverse demand assuming own-price elasticity is infinite. 
An asterisk denotes that the parameters were significant at 
the $p = 0.1$ level."

# demCap <- "Two-stage least-squares regression results when
# modeling demand (catch/quant supplied is the response variable). An 
# asterisk denotes that the parameters were significant at the p = 0.1 level."



csasdown::csas_table( invDemTable, escape = FALSE,
                      booktabs = TRUE, font_size = 10,
                      format = kableFormat,
                      caption = invDemCap,
                      align = rep("l",5)) %>%
  kable_styling(latex_options = c("striped", "hold_position","scale_down"),
                bootstrap_options = c("striped", "hover")) %>%
  add_header_above( header = c( " " = 1,
                                "Inv demand" = 2),
                    bold = TRUE)

  # csasdown::csas_table( demTable, escape = FALSE,
  #                     booktabs = TRUE, font_size = 10,
  #                     format = kable_format,
  #                     caption = demCap,
  #                     align = rep("l",5)) %>%
  # kable_styling(latex_options = c("striped", "hold_position","scale_down"),
  #               bootstrap_options = c("striped", "hover")) %>%
  # add_header_above( header = c( " " = 1,
  #                               "Demand" = 3),
  #                   bold = TRUE)



```

# Appendix B: Assessment error simulation

# Appendix C: Catchability and effort

The optimal allocation of effort in each area $p$, derived under equilibrium
reference point calculations, is very close to the ratio $\rho_p$ of inverse 
average catchabilty scalars within an area $p$ to the sum of inverse average 
catchabilities, i.e.,
\begin{align*}
\rho_p &= \frac{1/\bar{q}^{(F)}_p}{\sum_p 1/\bar{q}^{(F)}_p}, \\
\bar{q}^{(F)}_p & = \frac{1}{3} \sum_s q^{(F)}_{s,p}. \\
\end{align*}
Further, the optimal equilbrium allocation is also very close to the 
$E_{MSY,MS}$ allocation (Table 5), but the pattern does not hold for 
stochastic simulations under time-varying demand, as explained in 
the results.


<!-- 
An earlier version of this work included simulations where stochastic optima
were estimated with and without correlation in price and recruitment. 
Optimal harvest rates were then used, as above, as targets in closed loop 
simulations, cross tested against OM scenarios with and without the same 
correlation. While simulated correlation in recruitment and price deviations 
affected the distribution of fishery outcomes (e.g., NPV, biomass), there 
was little effect on the estimates of optimal harvest rates, and 
even less effect on the relative conservation and economic risks when
harvest rates derived from "incorrect" correlation scenarios were used to
set TACs. Such insensitivity to correlation is consistent with other 
studies showing that that the effects of synchrony (i.e., correlation) in 
recruitment process deviations among groundfish were dampened by their 
long-lived nature [@oken2020effects], as standing stocks of biomass and 
longer fishery recruitment delays almost completely compensate for 
recruitment variability, reducing risks associated with ignoring 
correlation. However, we do not assert that recruitment correlation among 
species and areas is not an important issue in spatial and multi-species 
fisheries management, as effects of correlation in the simulated DER
complex are likely limited by the lack of ecological interactions among
species and/or movement of stocks among areas. Recruitment correlation 
would probably have more significance in multi-stock contexts that include 
spatial movement, where TACs in one area could affect the effective harvest 
rate induced by another area's TACs through stock mixing 
[@goethel2016incorporating]. For example, there are two spawning stocks
for Atlantic Bluefin Tuna that differ in size by an order of magnitude
[ref]. Tuna catch limits in the eastern Atlantic ocean directly impact the 
escapement of fish from the larger Mediterranean spawning stock to the western 
Atlantic, which dilutes the harvest rates on the smaller Gulf of Mexico 
spawning stock. If recruitment to each stock was, for example, positively 
correlated, then harvest strategies that were designed to take advantage 
uncorrelated recruitments and high average proportions of Mediterranean 
spawners in the west Atlantic could, in years where both stocks are
affected by much lower than expected recruitment, take higher than 
expected quantities of Gulf spawners, increasing the risk of overfishing. 
In general, higher absolute correlation in recruitments would likely 
strengthen feedback links between areas, creating 
more significant differences between target harvest rates derived under 
correlated and uncorrelated scenarios. Recruitment correlation would also 
play a larger role for short-lived species, such as invertebrates 
[@oken2020effects; @dichmont2006management3], or if it was explicitly 
considered in a model-based biomass estimation procedure, affecting
TACs through stock status estimates [@dichmont2006management3]. -->