\clearpage
\setcounter{table}{0}  
\renewcommand{\thetable}{S\arabic{table}} 
\setcounter{figure}{0} 
\renewcommand{\thefigure}{S\arabic{figure}}

```{r suppCaps, echo = FALSE, include = FALSE}
econDataFigCap <- "Catch and ex-vessel unit price data for DER complex
species from 2006 to 2016. Prices are adjusted to 2016 prices assuming a
2\\% annual inflation rate."

idxResidsCap <- "Standardised residuals for commercial CPUE and survey 
trawlable biomass indices."

FvsEffCap <- "Maximum likelihood estimates of fishing mortality (vertical
axis) plotted against commercial trawl effort (horizontal axis) for
each area and species. Lines show the linear catchability scalar between 
fishing effort and fishing mortality for each species within an area,
used for simulating fishing post 2016."

postChainDiagCap <- "Histograms of posterior chain Rhat values (top left),
effective sample size (top right), and coefficients of variation (bottom
left). Vertical red lines show Rhat and effective sample size thresholds
for leading model parameters."

ssRefPtsInfPEDTabCap <- "Maximum likelihood estimates of maximum sustainable
multispecies yield ($MSY_{MS}$) and maximum economic yield ($MEY$) 
reference points for the British Columbia DER complex of flatfish
when price elasticity of demand was infinte (i.e. horizontal demand
curves). Effort (1000s of trawl hours) and rent (millons CAD\\$) are 
calculated by area, while catch ($MSY$, $C_{MEY}$, kt), biomass ($B_{MSY}$, 
$B_{MEY}$, kt), and harvest rate ($U_{MSY}$, $U_{MEY}$, unitless) 
are calculated by species within an area."

```


# DER complex demand analysis



The unit price $v_s$ ($/kg) of each species $s$ followed a downward sloping 
inverse demand curve for total species $s$ catch
\begin{equation} 
v_{s}(\sum_{p} C_{s,p}) = v^*_{s} \left( \frac{\sum_p C_{s,p}}{ \sum_p MSY_{SS,s,p}}  \right) ^{1/\lambda_s}
\end{equation}
where $v^*{s}$ was the 2016 reference price of species $s$ when catch 
was the sum of single-species MSY for each area, and $\lambda_s < 0$ is 
the price elasticity of demand [@varian1992microeconomic]. The price 
elasticity of demand $\lambda_s$ and 2016 reference price $v^*_s$ were 
found by fitting a time-varying inverse demand curve to average ex-vessel 
prices and catch data between 2006 and 2016 (see Appendix B). Modeling 
price as a decreasing function of quantity supplied captured the incentive 
of harvesters to reduce catch and keep prices higher through artificial 
scarcity, which results in a transfer of benefits (surplus) from consumers 
to producers [@pascoe2018offsetting]. 


\blandscape

```{r figS1-econData, echo = FALSE, warning = FALSE, fig.cap = econDataFigCap, fig.width = 7, out.width = "9in" }
figPath <- file.path("./figure/figS1-econData.pdf")
if(params$redoPlots)
{
  graphics.off()
  pdf(file = figPath, width = 7/fig_asp, height = 7 )
  plotPriceCatchTS()
  dev.off()
}
knitr::include_graphics(figPath)
```

\clearpage





# Assessment model goodness of fit



```{r fig4-idxResids, echo = FALSE, warning = FALSE, fig.cap = idxResidsCap, fig.width = 7, out.width = "9in" }
figPath <- file.path("./figure/fig4-idxResids.pdf")
if(params$redoPlots)
{
  graphics.off()
  pdf(file = figPath, width = 7/fig_asp, height = 7 )
  plotIdxResidsGrid( reports)
  dev.off()
}
knitr::include_graphics(figPath)
```

\elandscape


```{r ageFitAvg, echo = FALSE, fig.cap = "ageFitAvgDover HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 1, pIdx = 1,
                            sex = "female",
                            comps = "age"  )
```

\clearpage

```{r ageFitAvg2, echo = FALSE, fig.cap = "ageFitAvgEnglish HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 2, pIdx = 1,
                            sex = "female",
                            comps = "age" )
```

\clearpage

```{r ageFitAvg3, echo = FALSE, fig.cap = "ageFitAvg Rock HSHG"}

plotCompFitAvg( repObj = repObj,
                            initYear = 1956,
                            sIdx = 3, pIdx = 1,
                            sex = "female",
                            comps = "age" )
```

\clearpage

```{r postChainDiagnostics, echo = FALSE, fig.cap = postChainDiagCap}
plotMCdiagnostics(fitObj = reports)

```

\clearpage

```{r fig6-commEffFits, echo = FALSE, warning = FALSE, fig.cap = FvsEffCap }
figPath <- file.path("./figure/fig6-commEffFits.pdf")
if(params$redoPlots)
{
  graphics.off()
  pdf(file = figPath, width = 8.5, height = 11 )
  plotFvsEffHist_p( simObj, fIdx = 2, iRep = 1)
  dev.off()
}
knitr::include_graphics(figPath)
```

\clearpage

# Steady state equilibria with constant price
\blandscape
```{r ssRefPtsTable, echo = FALSE, warning = FALSE}
.loadSim(sim = "sim_infPED", baseDir = params$baseDir )
statRefPts <- makeStatMSEqbriaTab(blob)
ssRefPtsTab_infPED <- statRefPts

colnames(ssRefPtsTab_infPED) <- c( "Stock",
                            "Species",
                            "$q^F$",
                            "$E_{MSY}$",
                            "$\\pi \\left( \\sum MSY_{MS} \\right)$",
                            "$MSY_{MS}$",
                            "$B_{MSY,MS}$",
                            "$U_{MSY,MS}$",
                            "$E_{MEY}$",
                            "$MEY$",
                            "$C_{MEY}$",
                            "$B_{MEY}$",
                            "$U_{MEY}$")

ssRefPtsTab_infPED[,3] <- NULL

csasdown::csas_table( ssRefPtsTab_infPED, escape = FALSE,
                      booktabs = TRUE, font_size = 10,
                      format = kable_format,
                      # linesep = "\\addlinespace",
                      caption = ssRefPtsInfPEDTabCap,
                      align = c( "l", "l", rep("c",ncol(ssRefPtsTab_infPED)-2))) %>%
  kable_styling(latex_options = c("striped", "hold_position","scale_down"),
                bootstrap_options = c("striped", "hover"))  %>%
  add_header_above( header = c( " " = 2,
                                "DER complex maximum yield" = 5,
                                "Maximum Economic Yield" = 5),
                    bold = TRUE)

```


\elandscape