# Results

```{r loadInfoFiles, echo = FALSE, include = FALSE, warning = FALSE}
# Now read in all the info files
info.df <- readBatchInfo(batchDir = projDir) %>%
      mutate( blobPath = "", 
              perfTabPath = "", 
              lossBlobPath = "" )
# Update paths for each RData file and perf 
# table file
for( simIdx in 1:nrow(info.df))
{
  simLabel <- info.df$simLabel[simIdx]

  info.df$blobPath[simIdx]     <- file.path(projDir, simLabel, paste(simLabel,".RData",sep = "") )
  info.df$perfTabPath[simIdx]  <- file.path(projDir, simLabel, "simPerfStats.csv" )
  info.df$lossBlobPath[simIdx] <- file.path(projDir, simLabel, "loss.RData" )
}


```

## Omniscient manager simulations and multispecies equilibria

```{r loadOmni, echo = FALSE, include = FALSE, warning = FALSE}
omniInfo <- info.df %>% 
              filter( grepl( params$baseline, simLabel) )

# load performance table
omniPerfTab <- read.csv(omniInfo$perfTabPath)


```

We found that the median biomass of each species 
under the omniscient manager was close to the equilibrium 
biomass associated with the multispecies maximum 
sustainable yield in each area [figure]. Median
biomass, catch, and fishing mortality reach the equilbrium
soon after a transition period of about 20 years. During
the transitionary period, effort is slowly ramped up from
the level at the end of the historical period to a 
stationary distribution around each stock area's $E_{MSY}$.
In each area, as predicted by the equilibrium calculations, 
the optimal effort for the complex results in overfishing 
of the Dover sole stocks. 

Despite the tendency of the manager to increase fishing
mortality rates to above the single species $F_{MSY}$
for all Dover sole stocks, very few simulations actually push 
Dover sole into an overfished state. For all stocks of all 
species, the probability of being below 40% of single species
$B_{MSY}$ is at most 1% (TABLE), while probability of being
above 80% of $B_{MSY}$ is at least 53%. 

Tendency to reduce effort to very low in first few years
for some replicates, despite penalty in objective 
function -- check sims??


## MP performance


### Yield loss


### Biomass loss



## Sensitivity to prior distributions
