# Results

```{r loadInfoFiles, echo = FALSE, include = FALSE, warning = FALSE}
# Now read in all the info files
info.df <- readBatchInfo(batchDir = projDir) %>%
      mutate( blobPath = "", 
              perfTabPath = "", 
              lossBlobPath = "" )
# Update paths for each RData file and perf 
# table file
for( simIdx in 1:nrow(info.df))
{
  simLabel <- info.df$simLabel[simIdx]

  info.df$blobPath[simIdx]     <- file.path(projDir, simLabel, paste(simLabel,".RData",sep = "") )
  info.df$perfTabPath[simIdx]  <- file.path(projDir, simLabel, "simPerfStats.csv" )
  info.df$lossBlobPath[simIdx] <- file.path(projDir, simLabel, "loss.RData" )
}


```

## Multi-species complex equilibria

We found that the optimal harvest rate and spawning-stock biomass 
from the multi-species complex yield curves followed a similar
pattern across the three stock areas (Figure 2). In all areas, 
the optimal fishing effort for the area led to a slightly higher 
optimal harvest rate for Dover sole when compared to the 
single-species optima. In contrast, both English and rock sole 
had slightly lower optimal harvest rates than their single-species 
optima. In the HSHG area, where all three species had the 
highest biomasses, the multi-species optimal effort lay close 
to the single-species optimal effort, meaning that there was
very little foregone yield for each species in order
to maximise the total complex yield. In contrast, the other 
two areas each had a species yield curve with a peak that 
was very far to the right of the peaks of the other two curves, 
indicating the much lower catchability scalar between 
effort and fishing mortality for English sole in QCS, 
and rock sole in WCVI. Although English (QCS) and rock (WCVI) soles 
are proportionally further under-exploited under the multi-species 
optimal effort than the least catchable species (rock sole) in HSHG, 
the yield lost to under-exploitation is trivial given the absolute 
size of each is an order of magnitude smaller than the larger
stocks in those areas.


## Omniscient Manager Performance

```{r loadOmni, echo = FALSE, include = FALSE, warning = FALSE}
omniInfo <- info.df %>% 
              filter( grepl( params$baseline, simLabel) )

# load performance table
omniPerfTab <- read.csv(omniInfo$perfTabPath)


```



We found that the median biomass of each species 
under the omniscient manager was close to the equilibrium 
biomass associated with the multispecies maximum 
sustainable yield in each area [Figure 3, blue dashed line]. 
Median biomass, catch, and fishing mortality reach the equilbrium
soon after a transition period of about 20 years. During
the transitionary period, effort is slowly ramped up from
the level at the end of the historical period to a 
stationary distribution around each stock area's $E_{MSY}$
[Figure 4 - ADD]. In each area, as predicted by the 
equilibrium calculations, the optimal effort for the 
complex results in a slight overfishing of the Dover sole 
stocks. 

Despite the tendency of the manager to increase fishing
mortality rates to above the single species $F_{MSY}$
for all Dover sole stocks, very few simulations actually push 
Dover sole into an overfished state. For all stocks of all 
species, the probability of being below 40% of single species
$B_{MSY}$ is at most 6% , while probability of being
above 80% of $B_{MSY}$ is at least 53% (Table 2). 

Although the flatfish stocks we modeled are in an overall
healthy state and behave like developing fisheries, 
there are some cases where the omniscient manager reduced
fishing effort to historic low levels early in the projection 
period (Figure 4). These historic low efforts led to some years
where catch was below the minimum observed level (Table 2 - ADD). 
Low fishing effort was required in some replicates and years 
to protect the spawning stock and ensure production in 
later time steps where recruitment process error deviations 
were sustained at low levels. We attempted bounding effort 
below by the minimum observed historical effort to avoid 
simulations where effort was economically unviable, but this
increased the probability of catch being below the historical
minimum for each stock than the simulations we are presenting
with a lower bound of 0 effort.


## Management Procedure performance

Mangement Procedure performance is outlined below. We first
discuss the yield loss distributions for the 30 simulations,
then the spawning biomass loss distributions. Given the highly
factorial nature of the experiments, we explain the main results
using a few key examples in the main body of the text, but refer
readers to the online supplement for the full set of plots 
comparing stochastic simulations to the omniscient manager
scenarios.



### Yield loss

We found that the single-stock assessment methods had 
the lowest median loss across all stock areas, species, 
and aggregation levels under all three CV scenarios (Figure 6). 
As CVs increased, the single-stock method's catch loss was also
fairly stable, going from a median value of around 5 kt
for the whole coast-wide DER complex at a CV multiplier of
0.5 to a median around 12 kt at a multiplier of 2.0. In
contrast, the largest jump was observed under the 
Total Aggregation management procedures, which 
jumped from around 7 kt median loss to around 28 kt median 
loss.

The superior performance of single stock methods under 
absolute loss is caused in part by system dynamics
compensating for large assessment errors. Specifically, 
the single-stock assessments for five English and rock sole
stocks (all but HSHG rock sole) were positively biased
for large parts of the projection period, which in
turn produced unsustainably high TACs (Figure 6). 
Despite the high TACs, all five stocks with large assessment 
errors were actually fished at much closer to the optimal 
level, which happened when when TACs for more catchable 
stocks were fully caught (Figure 7). The key 
quality that made the choking off a net benefit (reduced
loss) was that the more catchable stocks (Dover and rock soles) 
had smaller assessment errors (Figure 8, Dover sole in
all three areas, and HSHG rock sole), and so the TACs were 
for those species were set based on harvest rates that were closer 
to the optimal yield for the complex. 

There was not a large difference in median loss values
between single-species ($F_{MSY}$) and multi-species ($E_{MSY}$)
harvest rates for most MPs and scenarios. Those MPs with
median catch loss values outside of the interquartile range of 
the other MPs with the same AM structure were data-pooled and 
hierarchical multi-stock MPs for WCVI rock sole, under the 
0.5obsErr and 1.0obsErr scenarios, respectively (Figure 5, 
WCVI rock sole). For the data-pooled MPs, the higher catch loss 
is from a persistent positive assessment error in the data-pooled
assessments (Figure). Because the multi-species harvest rates derived
from optimal effort $E_{MSY}$ are lower than the single-species
$U_{MSY}$ rates for WCVI rock sole, this leads to a higher 
catch loss when TACs are apportioned among species in the WCVI
area [Maybe compare relative TACs over time for WCVI DP]. 
For the hierarchical multi-stock MPs, the difference 
is more subtle but based on a similar phenomenon: 
assessment errors were very similar between target HRs, but 
lower target harvest rates led to a lower median loss 
(figure - maybe compare the three HRs, omni vs the SS/MS 
target HRs). Although these differences are large relative 
to the other MPs for this particular stock, the scale is very small in
an absolute sense, given the integration of losses over
a ten year period, and the small size of the WCVI rock sole stock
relative to the larger stocks in the complex.
As a result, the aggregate losses which include WCVI
rock sole are more similar between target harvest rates 
(Figure 5, WCVI data-pooled and coast-wide rock sole).

As observation error standard deviations increased, most 
MPs had higher catch loss, with two exceptions. Data pooled MPs 
for HSHG and WCVI rock sole stocks actually reduced catch
loss between 0.5obsErr and 1.0obsErr scenarios (Figure 5,
HSHG and WCVI rock sole). For these two stocks, assessment
errors are smaller under the 1.0obsErr scenario (overlay
plot with both scenarios' assessment errors), which
led to stock-specific TACs being set closer to the 
optimal level. [overlay plot??]
**CHECK ON ALLOCATION UNDER THE obsErr SCENARIOS,
the following is hypothetical at this stage**
The second factor is the allocation rule, which allocates
TACs to member stocks in a data-pooled stock area in 
proportion to their indices. Under lower observation
error standard deviations indices are less variable
so TACs are more dependent on the relative sizes
of the stocks and the synoptic survey trawl efficiency
valess... while under higher CVs the indices are more 
variable... will have to look at the plots...


***OUTLINE BELOW***

- Data pooling is the worst at low CVs, while total aggregation
is the worst at high CVs. Hypothesis: it's an interaction
of two things (i) variances add, so more aggregation
adds more variance, and (ii) TAC allocation method
is sensitive to higher CVs
- At 0.5 and 1.0 CV multiples, there is very little separation of 
any MPs. It's only when CVs get out to 2.0 times 
that we start to see the separation. 
- WCVI Rock sole bucks the trend: DP AMs with SS HRs tend do do 
uniformly badly across the 3 CV levels, with perhaps a small
improvement in median loss. On the other hand, the MS HRs
tend to degrade as expected with increasing CVs. Similar effect 
seen in HSHG Rock, and in the coastwide loss.
- Hierarchical multi-stock method's loss bridges between single-stock
and aggregation methods. For example, at low CVs the hierarchical
method tends to do about the same as the ssingle stock methods, but loss
increases more than the SS method with higher CVs. In general, the
HMS method ranks about the same across sspecies, stocks, and aggregation
levels, but at 2.0 CV multiples, HMS is closer to SS for WCVI,
closer to DP in HSHG, and around the middle in QCS. Overall, because
the HSHG stocks are the most populous, the HMS method has median loss
close to the DP method.
- When considering deviations from the optimal yield, ignoring stock 
structure and pooling at a coast-wide level was not advisable as
data quality is degraded. Both the CW and TA methods had the highest
loss, with similar median values for all species, stocks, and aggregation
levels.





### Biomass loss

Figures 7 and 8

As in yield loss, harvest rates did not a make significant difference
to median biomass loss.

Single stock methods still do better - (perhaps it is tuned to well to 
higher CVs)?

Less uniform ranking of AMs. In QCS and HSHG, HMS model tends to
have the highest loss at low CVs, then comes in to second lowest loss
at high CVs - stability of method as information is removed? In WCS,
some methods have lower biomass loss as CVs increase.

Interestingly, very little difference between MPs for loss in WCVI,
except CW and TA are very bad at higher CVs.

Again, not advisable to ignore spatial stock structure as data
quality reduces.

Need to look at simulation envelopes to understand the nature of
the loss - often underfishing, esp. as CVs increase.


Seems like SS does better on catch and biomass loss, but has
the tendency for large assessment errors. Although in this case
this is mitigated by the technical interactions in the system, where 
the most catchable (Dover sole) TACs get filled first and they happen 
to be set to a better level, this is system dependent. Indeed, 
a change in catchability due to switching the target species, or 
an underyling regime shift, could suddenly make it easier to fulfil
TACs that are set too high by a . 



## Sensitivity to prior distributions


