\clearpage
\setcounter{table}{0}
\setcounter{figure}{0}

# (APPENDIX) Appendices {-}

# The operating model

The operating model was a standard age- and sex-structured 
operating model, with additional structure for multi-species 
and multi-stock population dynamics. DER complex species and 
stocks were simulated assuming no ecological interactions or 
movement between areas. The lack of movement may be unrealistic, 
especially for Dover Sole given their extent, but this is how 
the the DER complex stocks are currently managed in practice. 
The lack of ecological interactions is more realistic for Dover 
and English soles, as although both species are benthophagus, 
there is evidence that they belong to different feeding guilds
[@pikitch1987use].

DER complex abundance $N_{a,x,s,p,t}$ for age $a$, sex $x$, 
species $s$ and stock $p$ at the start of year $t$ was
given by 
\begin{equation*}
N_{a,x,s,p,t} = \left \{ \begin{array} {ll}
                          0.5 R_{s,p,t}  & a = 1, \\
                          N_{a-1,x,s,p,t-1} \cdot e^{-Z_{a-1,x,s,p,t-1}} & 1 < a < A, \\
                          N_{a-1,x,s,p,t-1} \cdot e^{-Z_{a-1,x,s,p,t-1}} + N_{a,x,s,p,t-1}\cdot e^{-Z_{a,x,s,p,t-1}} & a = A^{(s)},
                          \end{array}
                \right.
\end{equation*}
where $R_t$ is age-1 recruitment in year $t$, $Z_{a,x,s,p,t}$
is the instantaneous total mortality rate, and $A^{(s)}$ is the plus
group age for species $s$.

Numbers-at-age were scaled to biomass-at-age by sex/species/area-
specific weight-at-age. Weight-at-age was an allometric function
of length-at-age
\begin{equation*}
w_{a,x,s,p} = \alpha_{x,s,p} \cdot L_{a,x,s,p}^{\beta_{x,s,p}}
\end{equation*}
where $\alpha_{x,s,p}$ scaled between cm and kg, $\beta_{x,s,p}$
determined the rate of allometric growth, and $L_{a,x,s,p}$ was
the length in cm of a fish of age $a$, sex $x$, species $s$ and 
stock $p$. Length-at-age was given by the following Schnute 
formulation of the von-Bertalanffy growth curve [@schnute1981versatile; 
@francis2016estimating] 
\begin{equation*}
L_{a} = \overline{L}_{A_1} - (\overline{L}_{A_2} - \overline{L}_{A_1}) \cdot 
            \left( \frac{e^{-k A_1} - e^{-k a} )} {e^{-k A_1} - e^{-k A_2} } \right) 
\end{equation*}
where $A_1$ and $A_2$ are well spaced reference ages, 
$\overline{L}_{A_1}$ and $\overline{L}_{A_2}$ are the mean lengths
in cm of fish at ages $A_1$ and $A_2$, and $k$ is the 
growth coefficient. Note that in the growth model we dropped the sex, 
species and stock subscripts for concision.

The maturity-at-age ogive was modelled as a logistic function
\begin{equation*}
m_{a,s,p} = \left( 1 + e^{-\frac{\ln 19 (a - a_{50,s,p}^{mat})}{a_{95,s,p}^{mat} - a_{50,x,s,p}^{mat}}}\right)^{-1},
\end{equation*}
where $m_{a,s,p}$ was the proportion of age-$a$ female fish 
of species $s$ in stock $p$ that were mature, and $a_{50,s,p}^{mat}$ 
and $a_{95,s,p}^{mat}$ are the ages at which 50\% and 95\% of fish 
of age-$a$, species $s$ and stock $p$ were mature.

Female spawning stock biomass was calculated as
\begin{equation*}
B_{s,p,t} = \sum_{a} N_{a,x',s,p,t} m_{a,s,p} w_{a,x',s,p},
\end{equation*}
where $x'$ denotes female fish only. Spawning stock biomass
was used to calculate expected Beverton-Holt recruitment, which
then had recruitment process errors applied
\begin{equation*}
R_{s,p,t+1} = \frac{R_{s,p,0} \cdot 4h_{s,p} \cdot B_{s,p,t} }
                    { B_{s,p,0} \cdot (1 - h_{s,p} ) + (5h_{s,p} - 1) \cdot B_{s,p,t}  }
                    \cdot e^{\epsilon_{s,p,t+1} - 0.5\sigma_{R,s,p}^2},
\end{equation*}
where $R_{s,p,0}$ is unfished equilibrium recruitment, $B_{s,p,t}$
is the spawning stock biomass at time $t$, $B_{s,p,0}$ is unfished spawning
stock biomasss, $h_{s,p}$ is stock-recruit steepness (average proportion
of $R_{s,p,0}$ produced when $B_{s,p,t} = .2B_{s,p,0}$), and
$\epsilon_{s,p,t}$ is the recruitment process error with standard 
deviation $\sigma_{R,s,p}$.

The operating model was initialised in 1956 at unfished equilibrium
for all species $s$ and areas $p$, with numbers-at-age in 1956
given by
\begin{equation*}
N_{a,x,s,p,1956} = \left \{ \begin{array} {ll}
                          0.5 R_{s,p,0}  & a = 1, \\
                          N_{a-1,x,s,p,1956} \cdot e^{-M_{x,s,p}} & 1 < a < A, \\
                          N_{a-1,x,s,p,1956} \cdot \frac{e^{-M_{x,s,p}}}{1 - e^{-M_{x,s,p}}} & a = A^{(s)},
                          \end{array}
                \right.
\end{equation*}

Fishery removals were assumed to be continuous throughout the year, 
with fishing mortality-at-age
\begin{equation*}
F_{a,x,s,p,f,t} = S_{a,x,s,p,f} \cdot F_{s,p,f,t},
\end{equation*}
where $F_{s,p,f,t}$ is the fully selected fishing mortality rate for
fleet $f$ at time $t$, and $S_{a,x,s,p,f}$ is the selectivity-at-age
$a$ for sex $x$ in species $s$ and area $p$ by fleet $f$. Selectivity-at
-age was modeled as a logistic function of length-at-age
\[
S_a = \left( 1 + \exp \left( \frac{-\ln 19 (L_a - l^{sel}_{50})}{l^{sel}_{95} - l^{sel}_{50}}  \right)   \right)^{-1},
\]
where $L_a$ is length-at-age, defined above, and $l^{sel}_{50}$
and $l^{sel}_{95}$ are the length-at-50\% and length-at-95\% selectivity,
respectively; stock, species and fleet subscripts are left off for concision.
Catch-at-age (in biomass units) was then found via the Baranov catch 
equation
\begin{equation*}
C_{a,x,s,p,f,t} = (1 - e^{-Z_{a,x,s,p,f,t}}) \cdot N_{a,x,s,p,t} w_{a,x,s,p} \frac{F_{a,x,s,p,f,t}}{Z_{a,x,s,p,f,t}},
\end{equation*}
where total mortality-at-age is defined as
\[
Z_{a,x,s,p,f,t} = M_{x,s,p} + S_{a,x,s,p,f} \cdot F_{a,x,s,p,f,t}.
\]

## Observation error standard deviations

Operating model observation error standard deviations were derived
from estimates from fitting a hierarchical age-structured model to 
DER complex data.


```{r loadSimForObsErrTable, echo = FALSE, include = FALSE}
.loadSim( 2, folder = params$groupFolder)

obsErrTableCap <- "Log-normal observation error standard deviations for all DER complex
biomass indices"

```

```{r obsErrTab, echo = FALSE}
tauObs_spf <- blob$ctlList$opMod$histRpt$tauObs_spf
tauObs_spf[tauObs_spf == 1] <- NA
tauObs_spf <- round(tauObs_spf,3)

tauObs.df <- reshape2::melt(tauObs_spf)

tauObs.df <- reshape2::dcast( tauObs.df, species + stock ~ fleet, value.var = "value")

colnames(tauObs.df) <- c("Species","Stock","Historical", "Modern", "HS Ass.", "Syn")

kable(  tauObs.df[,-1], escape = FALSE,
        booktabs = TRUE,
        caption = obsErrTableCap,
        align = rep("l",ncol(tauObs.df)-1)) %>%
  kable_styling(latex_options = c( "hold_position"),
                bootstrap_options = c("striped", "hover")) %>%
  pack_rows( "Dover sole",1,3 ) %>%
  pack_rows( "English sole",4,6 ) %>%
  pack_rows( "Rock sole",7,9 ) %>%
  add_header_above(c(" " = 1, "Observation Error SD" = 4) )

```

\clearpage
# Omniscient Manager Optimisation

We defined penalty functions so that inside their respective 
desired regions the penalty was zero, and otherwise the penalty grew 
as a cubic function of distance from the desired region. For example, 
a penalty designed to keep a measurement $x$ above a the desired 
region boundary $\epsilon$ is of the form
\begin{equation}
\mathcal{P}(x , \epsilon) = \left\{
  \begin{array}{ll}
    0 & x \geq \epsilon, \\
    |x - \epsilon|^3 & x < epsilon. \\
  \end{array} \right. 
\end{equation}
This form has a several advantages over simple linear penalties, 
or a logarithmic barrier penalty [@srinivasan2008tracking]. First, 
the cubic softens the boundary threshold $\epsilon$, effectively
allowing a crossover if doing so favours another portion of the 
objective function. Second, unlike lower degree polynomials, cubic
functions remain closer to the $x$-axis when $|x-\epsilon| < 1$. 
Third, zero penalty within in the desirable region stops
the objective function from favouring regions far from the boundaries 
of penalty functions. In contrast, a logarithmic function would 
favour overly conservative effort series to keep biomass far from 
a lower depletion boundary. Finally, the cubic penalty function and its 
first two derivatives are continuous at every point $x$, allowing for
fast derivative-based optimisation methods.

We used a cubic spline of effort in each area to reduce
the number of free parameters in the optimisation. For each
area, 9 knot points were distributed across the full 40 year
projection, making them spaced by 5 years. We padded
the omniscient manager simulations by an extra eight
years over the stochastic simulations to avoid any
possible end effects of the spline entering the 
performance metric calculations. Effort splines
were constrained to be between 0 and 120 times the
operating model $E_{MSY,p}$, by replacing any value 
outside that range with the closest
value inside the range (i.e. negative values by *zero*,
large values by $120 E_{MSY_p}$).

\clearpage

