<!-- The following code should appear at the beginning of the first appendix.
(if you have one)
After that, all subsequent sections will be turned into appendices. -->

`r if(knitr:::is_latex_output()) '% begin csasdown appendix'`
`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

\clearpage

# Appendix A {#app:first-appendix}

```{r loadAppAFuns, echo = FALSE, include = FALSE }
source(here::here("docs/rebuildingPlan/figure/SISCAplots.R"))
source(here::here("docs/rebuildingPlan/figure/SISCArefPts.R"))

# load base OM
load(here::here('history/fit_MSbase_MCMC/fit_MSbase_MCMC.RData'))

```

This appendix includes plots for equilibrium relationships for 
reference points calculations, and,.... other parameter of interest 
for the base operating model

Figures and tables will now be prepended with the appendix letter:

(ref:test1) English version of the test1 figure caption

(ref:test1-french) French goes here

```{r refPtsCS, fig.pos="H", fig.cap = refPtsCSCap}
refPtsCSCap <- "Equilibrium relationships from the base operating model for Cumshewa/Selwyn showing a) Yield Per Recruit for increasing fishing mortality (F), b) Spawning biomass (SB) per recruit for increasing fishing mortality (F), c) Yield for increasing fishing mortality (F), d) Spawning biomass for increasing fishing mortality (F), e) Recruitment for different levels of spawning biomass, and f) Yield for different levels of spawning biomass. In all plots the green point indicates values at Fmsy."
plotRefPts_p(repList = reports, pIdx=1)
```

\clearpage 


```{r refPtsJPS, fig.pos="H", fig.cap = refPtsJPSCap}
refPtsJPSCap <- "Equilibrium relationships from the base operating model for Juan Perez/Skincuttle showing a) Yield Per Recruit for increasing fishing mortality (F), b) Spawning biomass (SB) per recruit for increasing fishing mortality (F), c) Yield for increasing fishing mortality (F), d) Spawning biomass for increasing fishing mortality (F), e) Recruitment for different levels of spawning biomass, and f) Yield for different levels of spawning biomass. In all plots the green point indicates values at Fmsy."
plotRefPts_p(repList = reports, pIdx=2)
```

\clearpage

```{r refPtsLou, fig.pos="H", fig.cap = refPtsLouCap}
refPtsLouCap <- "Equilibrium relationships from the base operating model for Louscoone showing a) Yield Per Recruit for increasing fishing mortality (F), b) Spawning biomass (SB) per recruit for increasing fishing mortality (F), c) Yield for increasing fishing mortality (F), d) Spawning biomass for increasing fishing mortality (F), e) Recruitment for different levels of spawning biomass, and f) Yield for different levels of spawning biomass. In all plots the green point indicates values at Fmsy."
plotRefPts_p(repList = reports, pIdx=3)
```

\clearpage

# Appendix B {#app:second-appendix}

The label `#app:` in the appendix section headers tell `csasdown` to start a new appendix, and the next letter in the alphabet will be used for the appendix, and prepended to figure and table names. For example, this appendix's whole section header looks like:


<!-- At the end of your appendices add: -->
`r if(knitr:::is_latex_output()) '% end csasdown appendix'`
